NIRCam Calibration Plan

### 2016-11-28 ms.tex
I added some more tweaks to the discussion of the ND filter and integration times needed.

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$)
Observing these bright sources (which are bright naked eye stars!) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
The same configuration can then be used on

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp}$\\
\hline \hline
1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 		& -1.35		& On	&	32$\times$32	& F466N	& \\
2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W  &  \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W  &  \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
\vspace{0.05in}
\end{table}

@@

There are several ways to improve saturation limits:
\begin{itemize}
\item Cut down the aperture size with a Lyot stop. These have 19\% throughput, but make the PSF shapes strange.
\item Use a neutral density square in the coronagraph mask. The neutral density filters have an attenuation of around 10$^3$ or 7.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region
\item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square
\item Use a narrowband filter, such as F121N
\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
\end{itemize}

>>>>

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$).
Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
The same configuration can then be used on

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp} (s) $\\
\hline \hline
1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 V		& -1.35		& On	&	32$\times$32	& F466N	& 0.1 \\
2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame	& F466N  &  \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Frame  	& F444W  &  \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
\vspace{0.05in}
\end{table}

@@

There are several ways to improve saturation limits:
\begin{itemize}
\item Cut down the aperture size with a Lyot stop. These have 19\% throughput, but make the PSF shapes strange.
\item Use a neutral density square in the coronagraph mask. The neutral density filters have an attenuation of around 10$^2.6$ or 6.5 mags. A color correction would have to be applied for the neutral density filter (since it is wavelength dependent) when transferring to an un-occulted region. Additionally, the Lyot stop that must be in place to use the neutral density filter has a throughput of 19\%, so the total improvement is 8.3 mags
\item Use a long wavelength grism to spread out the light - this could be used in conjunction with a neutral density square
\item Use a narrowband filter, such as F121N
\item Use a small subarray - 64 $\times$ 64 is supported for science. There will be an engineering jitter monitoring test with an 8 $\times$ 8 subarray 
\end{itemize}
